Meta-analysis of the Interoceptive Accuracy Scale (IAS)

### 2024-11-17 analysis/Stud1_a.qmd
let's not use gt
Minor: format links

---
title: "Meta-analysis of the Interoceptive Accuracy Scale"
subtitle: "Study 1"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: true
    toc: true
    fig-dpi: 100
    fig-width: 11.33
execute: 
  cache: true
---

@@

Murphy (<https://osf.io/3m5nh)>

@@

Gaggero (2021) (<https://osf.io/5x9sg)>

@@

Campos (2022) - Study 1 (<https://osf.io/j6ef3)>

@@

Todd (2022) - <https://osf.io/ms354/>

@@

Arslanova (2022) - <https://osf.io/mp3cy/>

@@

Brand (2022) - <https://osf.io/xwz6g/>

@@

Brand (2023) - <https://osf.io/3f2h6/>

@@

Lin (2023) - <https://osf.io/3eztd> - Note: No tickle because same Chinese character

@@

VonMohr (2023) - Study 3 (<https://osf.io/7p9u5/)>

@@

Makowski

-   Note: First sample has some missing items
-   Note: Analog scales

@@

library(gt)
library(tidyverse)

@@

table_apa <- apa_style(table_apa)

# Save as image for IPPE google docs workflow
gtsave(data = table_apa, path = "../paper/1_Initial/figures", filename = "table1.png")
```

>>>>

---
title: "Meta-analysis of the Interoceptive Accuracy Scale (IAS)"
subtitle: "Study 1"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: true
    toc: true
    fig-dpi: 100
    fig-width: 11.33
execute: 
  cache: true
---

@@

- Murphy (2020)
  - https://osf.io/3m5nh

@@

- Gaggero (2021) 
  - https://osf.io/5x9sg

@@

- Campos (2022) - Study 1 
  - https://osf.io/j6ef3

@@

- Todd (2022) 
  - https://osf.io/ms354/

@@

- Arslanova (2022)
  - https://osf.io/mp3cy/

@@

- Brand (2022) 
  - https://osf.io/xwz6g/

@@

- Brand (2023) 
  - https://osf.io/3f2h6/

@@

- Lin (2023)
  - https://osf.io/3eztd
  - Note: No tickle because same Chinese character

@@

- VonMohr (2023) - Study 3 
  - https://osf.io/7p9u5/

@@

- Makowski
  - Note: First sample has some missing items
  - Note: Analog scales

@@

library(gt)

@@

table_apa <- apa_style(table_apa) 
table_apa
```
